Diagnostics Week of June 28th

### 2020-07-08 output_scripts/Diagnostics.Rmd
add some further plots

>>>>

# Latent Ranks vs Expert Ranks

```{r}
for(current_cohort in 1:10) {
  #cat("Cohort, ", current_cohort,"\n",sep="")
  load(paste(data_path,cohort_names[current_cohort],
             "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
             ".RData",sep=''))

  mean_latent_rank <- apply(sim_cohort_mmhp$f,2,mean)

  ranks <- tibble(expert = expert_rank_10[[current_cohort]],
                  latent = mean_latent_rank)

  p <- ggplot(ranks,aes(latent,expert)) + geom_point() + 
    scale_y_continuous(breaks = c(12:1), trans = "reverse") + 
    ggtitle(paste("Cohort ", current_cohort,sep=""))
  print(p)
}

# Ranks vs Degree

```{r}

for(current_cohort in 1:10) {
  cat("Cohort, ", current_cohort,"\n",sep="")
  load(paste(data_path,cohort_names[current_cohort],
             "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
             ".RData",sep=''))

  mean_latent_rank <- apply(sim_cohort_mmhp$f,2,mean)

  ranks <- tibble(expert = expert_rank_10[[current_cohort]],
                  latent = mean_latent_rank)
  out_degree <- apply(sim_cohort_mmhp$gamma,2,mean)
  in_degree <- apply(sim_cohort_mmhp$zeta,2,mean)

  degs <- tibble(expert = expert_rank_10[[current_cohort]],
                  latent = mean_latent_rank,
                 out_deg = out_degree,
                 in_deg = in_degree)

  p <- ggplot(degs,aes(latent,out_deg)) + geom_point() + 
    #scale_y_continuous(breaks = c(12:1), trans = "reverse") + 
    ggtitle(paste("Out Degree vs Latent Cohort ", current_cohort,sep="")) + 
    ylab("Out Degree") + xlab("Latent Rank")
  print(p)

  q <- ggplot(degs,aes(latent,in_deg)) + geom_point() +
    ggtitle(paste("In Degree vs Latent Cohort ",current_cohort,sep="")) +
    ylab("In Degree") + xlab("Latent Rank")
  print(q)

  r <- ggplot(degs,aes(expert,out_deg)) + geom_point() +
    ggtitle(paste("Out Degree vs Expert Cohort ", current_cohort,sep="")) + 
    ylab("Out Degree") + xlab("Expert Rank")
  print(r)

  s <- ggplot(degs,aes(expert,in_deg)) + geom_point() +
    ggtitle(paste("In Degree vs Expert Cohort ", current_cohort,sep="")) + 
    ylab("In Degree") + xlab("Expert Rank")
  print(s)

}
